[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-08-01 paper/paper.qmd
started sentiment analysis (fun!)

```{r setup, include=FALSE}

## Workspace Setup ##

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)
library(quanteda)

@@

The wide release of ChatGPT and other Large Language Models (LLMs) has rapidly transformed various parts of society, in particular the field of education. As these tools are increasingly accessible, their adoption and use in academic settings has created excitement and apprehension among educators and students alike. LLMs offer unprecedented support for students in tasks ranging from writing assistance to support in complex problem-solving, with the potential to enhance academic performance and student outcomes. At the same time, their use raises questions about academic integrity, the development of critical thinking skills (particular in undergraduates), as well as questions about their implications for effective learning overall.

@@

As we have seen, the existing inquiry by educators has explored the general qualitative usage and student perceptions on these tools. Though informative, there is still a key lack of evidence of how students' academic performance can be affected through allowing them to use LLMs in classwork. This paper aims to fill this gap by quantitatively investigating the relationship between students' grades and measures of student LLM usage and their attitudes toward LLMs in general, using evidence from a third-year undergraduate statistics course at the University of Toronto. Through examining how students interact with and perceive LLM tools and how these variables translate into student outcomes, the effects of LLM integration in data science education can be more precisely determined.

@@

All the data was cleaned using R [@citeR] and it's tidyverse [@tidyverse], janitor [@janitor] and stringr [@stringr], then tested for issues using the testthat package [@testthat]. This led to a final dataset containing 121 responses across (var_num) variables.

These variables were:

- [list of variables]

## Visualization

The student survey data was then visualized and analyzed using the ggplot2 [@ggplot2] package.

### General Information

First, some general information about our sample of students was derived through visualizing the basic data about them.

@@

#Trim values to histogram

@@

plot_data |>
    ggplot(aes(x = mins_complete)) +
    geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
    labs(title = "Distribution of Survey Response Times",
         x = "Time (Mins)",
         y = "Frequency") +
    theme_minimal() +
    theme(plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5))

```
@fig-response-time-hist shows the distribution of response times to the end-of-course survey. Respondents who consented generally took between 0-40 mins to answer all of the questions, with most response times ranging between 2-10 minutes. There was one consenting respondent who took 4308 minutes, whose observation was dropped from the visualization. This suggests that students generally took a meaningful amount of time to engage with the survey.

@@

#Histogram of GPA

survey_data |>
    ggplot(aes(x = gpa)) +
    geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
    labs(title = "Distribution of Student GPA",
         x = "GPA",
         y = "Frequency") +
    theme_minimal() +
    theme(plot.title.position = "plot",
          plot.title = element_text(hjust = 0.6))

@@

# Display the original wide format table
kable(year_count)

@@

#Pie chart of program of study

@@

ggplot(program_counts, aes(x = "", y = n, fill = program_of_study)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Student Distribution by Program of Study",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  scale_fill_discrete(name="Program") +
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        axis.title.x = element_blank(), # Remove x-axis title
        plot.title = element_text(hjust = 1.6)
        ) +
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5))

Programs of study [did something], as we can see in @fig-programs-pie...

### Student Attitudes

@@

table_data <- survey_data |>
    select(ai_familiarity)|>
    mutate(
      ai_familiarity = case_when(
        ai_familiarity == "Limited to some liberal arts, such as history courses" ~ "Somewhat familiar",
        TRUE ~ ai_familiarity
      )
    ) |>
    count(ai_familiarity)

table_data |>
  ggplot(aes(x = "", y = n, fill = ai_familiarity)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Student Familiarity with AI",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  scale_fill_discrete(name="Program") +
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        axis.title.x = element_blank(), # Remove x-axis title
        plot.title = element_text(hjust = 1.35)
        ) +
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5)
            )
```

@@

#Select first three statements
writing_perceptions <- survey_data |>
  select(
    writing_is_easy_for_me, 
    i_like_to_write, 
    i_believe_it_is_important_to_be_a_good_writer
  )

@@

#Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Student Self-Perceptions on Writing",
       x = "Response",
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        legend.position= "bottom", 
      )

@@

# TODO: Fix label, Fix Legend title, Fix legibility of Response

@@

#Select first three statements
writing_perceptions <- survey_data |>
  select(
    coding_is_easy_for_me,
    i_like_to_code,
    i_believe_it_is_important_to_be_a_good_coder
  )

@@

#Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Student Self-Perceptions of Coding",
       x = "Response",
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        legend.position= "bottom", 
      )

@@

#Select first three statements
writing_perceptions <- survey_data |>
  select(
    when_i_check_my_code_it_is_easy_for_me_to_catch_my_mistakes, 
    i_feel_confident_sharing_my_code,
    i_am_confident_in_my_overall_coding_ability
  )

@@

#Pie chart of student opinion on appropriateness of AI use in class.

@@

ggplot(appropriate, aes(x = "", y = n, fill = ai_schoolwork_appropriate)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Do students think AI use is appropriate in class?",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  scale_fill_discrete(name="Response") +
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),  # Remove x-axis text
        axis.title.x = element_blank(),
      ) +
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5))

### Student Usage

@@

#Select first three statements
writing_perceptions <- survey_data |>
  select(
    used_ai_any_reason, 
    used_ai_in_sta302
  )

@@

#Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Student Self-Perceptions of Coding",
       x = "Response",
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
      )

@@

type_data <- survey_data |>
              select(
                not_used,
                used_technical_q,
                used_conversation,
                used_general_knowledge,
                used_solving_hmk,
                used_check_soln,
                used_quick_q,
                used_expl_concepts,
                used_writing_content,
                used_writing_code
              )|>
              pivot_longer(cols = everything(), names_to = "Statements", values_to = "Response") |>
              mutate(Statements = case_when(
                Statements == "not_used" ~ "Not Used",
                Statements == "used_technical_q" ~ "Technical Questions",
                Statements == "used_conversation" ~ "Fun Conversation",
                Statements == "used_general_knowledge" ~ "General Knowledge",
                Statements == "used_solving_hmk" ~ "Entirely Solving Homework",
                Statements == "used_check_soln" ~ "Checking my Solutions",
                Statements == "used_quick_q" ~ "Quick Questions",
                Statements == "used_expl_concepts" ~ "Explaining Concepts",
                Statements == "used_writing_content" ~ "Writing Paper Content",
                Statements == "used_writing_code" ~ "Writing Paper Code",
                TRUE ~ Statements
              )) |>
              filter(Response == 1) |>
              count(Statements) |>
              arrange(desc(n))

type_data |>
    ggplot(aes(x = n, y = reorder(Statements, n))) +
    geom_bar(stat="identity", fill="grey50") +
    labs(title="How Students Used ChatGPT", x="Count", y="Use Type") +
    theme_classic()

@@

type_data <- survey_data |>
              select(
                not_used,
                used_technical_q,
                used_conversation,
                used_general_knowledge,
                used_solving_hmk,
                used_check_soln,
                used_quick_q,
                used_expl_concepts,
                used_writing_content,
                used_writing_code
              )|>
              pivot_longer(cols = everything(), names_to = "Statements", values_to = "Response") |>
              mutate(Statements = case_when(
                Statements == "not_used" ~ "Not Used",
                Statements == "used_technical_q" ~ "Technical Questions",
                Statements == "used_conversation" ~ "Fun Conversation",
                Statements == "used_general_knowledge" ~ "General Knowledge",
                Statements == "used_solving_hmk" ~ "Entirely Solving Homework",
                Statements == "used_check_soln" ~ "Checking my Solutions",
                Statements == "used_quick_q" ~ "Quick Questions",
                Statements == "used_expl_concepts" ~ "Explaining Concepts",
                Statements == "used_writing_content" ~ "Writing Paper Content",
                Statements == "used_writing_code" ~ "Writing Paper Code",
                TRUE ~ Statements
              )) |>
              filter(Response == 1) |>
              count(Statements) |>
              arrange(desc(n))

type_data |>
    ggplot(aes(x = n, y = reorder(Statements, n))) +
    geom_bar(stat="identity", fill="grey50") +
    labs(title="How Students Used ChatGPT", x="Count", y="Use Type") +
    theme_classic()

@@

```{r senti-analysis}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Hello
#| fig-align: center

>>>>

```{r setup, include=FALSE}
## Workspace Setup ##

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)
library(tidyr)
library(tidytext)
library(textdata)
library(quanteda)

@@

The wide release of ChatGPT and other Large Language Models (LLMs) has rapidly transformed education at all levels and disciplines. Their quick adoption in academic settings has created excitement and apprehension among educators and students alike. LLMs offer unprecedented support for students in tasks ranging from writing assistance to support in complex problem-solving, with the potential to enhance academic performance and student outcomes. At the same time, their use raises important questions about academic integrity, the development of critical thinking skills (particular in undergraduates), as well as questions about their implications for effective learning overall.

@@

As we have seen, the existing inquiry by educators has explored the general qualitative usage and student perceptions on these tools. Though informative, a key question still remains: how can students' academic performance be affected, precisely, through allowing them to use LLMs in classwork?

This paper aims to fill this gap by quantitatively investigating the relationship between students' grades and measures of student LLM usage and their attitudes toward LLMs in general, using evidence from a third-year undergraduate statistics course at the University of Toronto. Through examining how students interact with and perceive LLM tools and how these variables translate into student outcomes, the effects of LLM integration in data science education can be more precisely determined.

@@

All the data was cleaned using R [@citeR] and it's tidyverse [@tidyverse], janitor [@janitor] and stringr [@stringr], then tested for issues using the testthat package [@testthat]. This led to a final dataset containing 121 responses across 41 variables that corresponded to each survey question.

## General Information

First, general information about the sample of students was derived first, through visualizing the basic data about them. This was done using the ggplot2 [@ggplot2] package.

@@

# Trim values to histogram

@@

plot_data |>
  ggplot(aes(x = mins_complete)) +
  geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Survey Response Times",
    x = "Time (Mins)",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5)
  )
```
@fig-response-time-hist shows the distribution of response times to the end-of-course survey. Respondents who consented generally took between 0-40 mins to answer all of the questions, with most response times ranging between 2-10 minutes. There was one consenting respondent who took 4308 minutes, whose observation was dropped from the visualization. This suggests that students generally took a meaningful amount of time to engage with the survey.

@@

# Histogram of GPA

survey_data |>
  ggplot(aes(x = gpa)) +
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Student GPA",
    x = "GPA",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.6)
  )
```

@@

# Display the original wide format table
kable(year_count)
```

@@

# Pie chart of program of study

@@

ggplot(program_counts, aes(x = "", y = n, fill = program_of_study)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(
    title = "Student Distribution by Program of Study",
    x = NULL,
    y = NULL
  ) +
  theme_minimal() +
  scale_fill_discrete(name = "Program") +
  theme(
    axis.text.x = element_blank(), # Remove x-axis text
    axis.title.x = element_blank(), # Remove x-axis title
    plot.title = element_text(hjust = 1.6)
  ) +
  geom_text(aes(label = n),
    position = position_stack(vjust = 0.5)
  )
```

Programs of study [did something; waiting on major/minor data], as we can see in @fig-programs-pie...

## Student Attitudes

@@

table_data <- survey_data |>
  select(ai_familiarity) |>
  mutate(
    ai_familiarity = case_when(
      ai_familiarity == "Limited to some liberal arts, such as history courses" ~ "Somewhat familiar",
      TRUE ~ ai_familiarity
    )
  ) |>
  count(ai_familiarity)

table_data |>
  ggplot(aes(x = "", y = n, fill = ai_familiarity)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(
    title = "Student Familiarity with AI",
    x = NULL,
    y = NULL
  ) +
  theme_minimal() +
  scale_fill_discrete(name = "Program") +
  theme(
    axis.text.x = element_blank(), # Remove x-axis text
    axis.title.x = element_blank(), # Remove x-axis title
    plot.title = element_text(hjust = 1.35)
  ) +
  geom_text(aes(label = n),
    position = position_stack(vjust = 0.5)
  )
```

@@

# Select first three statements
writing_perceptions <- survey_data |>
  select(
    writing_is_easy_for_me,
    i_like_to_write,
    i_believe_it_is_important_to_be_a_good_writer
  )

@@

# Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
  myPlot +
    guides(
      shape = guide_legend(override.aes = list(size = pointSize)),
      color = guide_legend(override.aes = list(size = pointSize))
    ) +
    theme(
      legend.title = element_text(size = textSize),
      legend.text = element_text(size = textSize),
      legend.key.size = unit(spaceLegend, "lines")
    )
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(
    title = "Student Self-Perceptions on Writing",
    x = "Response",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom",
  )

@@

# TODO: Fix label, Fix Legend title, Fix legibility of Response
```

@@

# Select first three statements
writing_perceptions <- survey_data |>
  select(
    coding_is_easy_for_me,
    i_like_to_code,
    i_believe_it_is_important_to_be_a_good_coder
  )

@@

# Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
  myPlot +
    guides(
      shape = guide_legend(override.aes = list(size = pointSize)),
      color = guide_legend(override.aes = list(size = pointSize))
    ) +
    theme(
      legend.title = element_text(size = textSize),
      legend.text = element_text(size = textSize),
      legend.key.size = unit(spaceLegend, "lines")
    )
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(
    title = "Student Self-Perceptions of Coding",
    x = "Response",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom",
  )

@@

# Select first three statements
writing_perceptions <- survey_data |>
  select(
    when_i_check_my_code_it_is_easy_for_me_to_catch_my_mistakes,
    i_feel_confident_sharing_my_code,
    i_am_confident_in_my_overall_coding_ability
  )

@@

# Pie chart of student opinion on appropriateness of AI use in class.

@@

ggplot(appropriate, aes(x = "", y = n, fill = ai_schoolwork_appropriate)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(
    title = "Do students think AI use is appropriate in class?",
    x = NULL,
    y = NULL
  ) +
  theme_minimal() +
  scale_fill_discrete(name = "Response") +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_blank(), # Remove x-axis text
    axis.title.x = element_blank(),
  ) +
  geom_text(aes(label = n),
    position = position_stack(vjust = 0.5)
  )
```

## Student Usage

@@

# Select first three statements
writing_perceptions <- survey_data |>
  select(
    used_ai_any_reason,
    used_ai_in_sta302
  )

@@

# Taken from: https://stackoverflow.com/questions/52297978/decrease-overal-legend-size-elements-and-text
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
  myPlot +
    guides(
      shape = guide_legend(override.aes = list(size = pointSize)),
      color = guide_legend(override.aes = list(size = pointSize))
    ) +
    theme(
      legend.title = element_text(size = textSize),
      legend.text = element_text(size = textSize),
      legend.key.size = unit(spaceLegend, "lines")
    )
}

# Make the plot
multi_bar <- writing_perceptions_long |>
  ggplot(aes(x = Response, fill = Statements)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(
    title = "Student Self-Perceptions of Coding",
    x = "Response",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5),
  )

@@

type_data <- survey_data |>
  select(
    not_used,
    used_technical_q,
    used_conversation,
    used_general_knowledge,
    used_solving_hmk,
    used_check_soln,
    used_quick_q,
    used_expl_concepts,
    used_writing_content,
    used_writing_code
  ) |>
  pivot_longer(cols = everything(), names_to = "Statements", values_to = "Response") |>
  mutate(Statements = case_when(
    Statements == "not_used" ~ "Not Used",
    Statements == "used_technical_q" ~ "Technical Questions",
    Statements == "used_conversation" ~ "Fun Conversation",
    Statements == "used_general_knowledge" ~ "General Knowledge",
    Statements == "used_solving_hmk" ~ "Entirely Solving Homework",
    Statements == "used_check_soln" ~ "Checking my Solutions",
    Statements == "used_quick_q" ~ "Quick Questions",
    Statements == "used_expl_concepts" ~ "Explaining Concepts",
    Statements == "used_writing_content" ~ "Writing Paper Content",
    Statements == "used_writing_code" ~ "Writing Paper Code",
    TRUE ~ Statements
  )) |>
  filter(Response == 1) |>
  count(Statements) |>
  arrange(desc(n))

type_data |>
  ggplot(aes(x = n, y = reorder(Statements, n))) +
  geom_bar(stat = "identity", fill = "grey50") +
  labs(title = "How Students Used ChatGPT", x = "Count", y = "Use Type") +
  theme_classic()
```

@@

type_data <- survey_data |>
  select(
    not_used,
    used_technical_q,
    used_conversation,
    used_general_knowledge,
    used_solving_hmk,
    used_check_soln,
    used_quick_q,
    used_expl_concepts,
    used_writing_content,
    used_writing_code
  ) |>
  pivot_longer(cols = everything(), names_to = "Statements", values_to = "Response") |>
  mutate(Statements = case_when(
    Statements == "not_used" ~ "Not Used",
    Statements == "used_technical_q" ~ "Technical Questions",
    Statements == "used_conversation" ~ "Fun Conversation",
    Statements == "used_general_knowledge" ~ "General Knowledge",
    Statements == "used_solving_hmk" ~ "Entirely Solving Homework",
    Statements == "used_check_soln" ~ "Checking my Solutions",
    Statements == "used_quick_q" ~ "Quick Questions",
    Statements == "used_expl_concepts" ~ "Explaining Concepts",
    Statements == "used_writing_content" ~ "Writing Paper Content",
    Statements == "used_writing_code" ~ "Writing Paper Code",
    TRUE ~ Statements
  )) |>
  filter(Response == 1) |>
  count(Statements) |>
  arrange(desc(n))

type_data |>
  ggplot(aes(x = n, y = reorder(Statements, n))) +
  geom_bar(stat = "identity", fill = "grey50") +
  labs(title = "How Students Used ChatGPT", x = "Count", y = "Use Type") +
  theme_classic()
```

```{r setup-sentiment}
#| message: false
#| echo: false
#| warning: false

#get positive words from NRC lexicon
pos_words <- get_sentiments("nrc") |>
  filter(sentiment = c("anger", "disgust", "fear", "negative", "sadness"))

#get negative words from NRC lexicon
neg_words <- get_sentiments("nrc") |>
  filter(sentiment = c("joy", "positive",
"surprise",
"trust", 
"anticipation"))
```

We then performed sentiment analysis on the free-response comment questions asked to students. To perform this text analysis, the tidytext package [@tidytext] was used in conjunction with the NRC word-emotion lexicon compiled by @mohammad. Although four lexicon options were available in tidytext, the NRC lexicon was chosen due to the relatively balanced amounts of positive and negative words in the dataset, allowing for balanced classification.

### Appropriateness of AI in Schoolwork

In the survey, students were asked to respond to the question: "Please elaborate on to what extent do you think using generative AI tools such as ChatGPT by OpenAI (or equivalents) is ethical and appropriate for schoolwork?".

```{r setup-ai-appropriate}

# AI Appropriateness Comments
ai_comments <- survey_data |>
  select(
    id,
    ai_schoolwork_appropriate_comments
  ) |>
  mutate(
    comment = ai_schoolwork_appropriate_comments
  ) |>
  select(-c(ai_schoolwork_appropriate_comments))

# put comments into tidytext format
tidy_ai_comments <- ai_comments |>
  group_by(id) |>
  unnest_tokens(word, comment)

@@

### Recommendations in STA302 
```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Hello
#| fig-align: center

recs_comments <- survey_data |>
  select(
    id,
    recs_for_ai_sta302
  )
```
